\documentclass[a4paper, landscape]{article}

% Used for wolf svg logo
\usepackage{pstricks}

\input{include/cardLibs.tex}
\input{include/cardColours.tex}
\input{include/cardStyles.tex}

% Shorthand commands for the different factions
\newcommand{\townsfolk}[3]{\materialcard{#1}{#2}{#3}{Townsfolk}}
\newcommand{\selfish}[3]{\materialcard{#1}{#2}{#3}{Selfish}}
\newcommand{\werewolf}[3]{\materialcard{#1}{#2}{#3}{Werewolves}}

% Some stock text for the repeated cards
\newcommand{\villagerDescription}{You are a weak, feeble, powerless villager, you're only hope is to convince others of your innocence. \par Many will claim to be you.\\ Good luck!}
\newcommand{\werewolfDescription}{Wake-up in the night to find your pack and work together to survive the day.\par If you find that you're a lonewolf, take a peek at a card from the centre during the night.}

\newcommand{\cardpage}[8]{\begin{center}#1\hspace{2mm}#2\hspace{2mm}#3\hspace{2mm}#4\\\vspace{5mm}#5\hspace{2mm}#6\hspace{2mm}#7\hspace{2mm}#8\end{center}}

\newcommand{\reversecardpage}{\cardpage{\cardreverse}{\cardreverse}{\cardreverse}{\cardreverse}{\cardreverse}{\cardreverse}{\cardreverse}{\cardreverse}}

\begin{document}
\pagestyle{empty}
% Syntax \affiliationName{ROLE_NAME}{HINT/JOKE}{ROLE_DESCRIPTION}
\cardpage{
\werewolf{Werewolf}
{Survive the day!}
{\werewolfDescription}{Yes}}
%
{\werewolf{Werewolf}
{Survive the day!}
{\werewolfDescription}{Yes}}
%
{\townsfolk{Villager}
{Hunt the wolves!}
{\villagerDescription}{No}}
%
{\townsfolk{Villager}
{Hunt the wolves!}
{\villagerDescription}{No}}
%
{\townsfolk{Seer}
{What do your elf eyes see?}
{Wake up in the night to view one other player's card, or two cards from the centre.

Choose the time to reveal what you saw wisely...}{Yes}}
%
{\townsfolk{Robber}
{Take what you can get.}
{You may swap your card for any other player's card; you can only view your new card after the swap. No take-backs!

You must assume the new role during the day phase.}{Yes}}
%
{\townsfolk{Trouble-maker}
{Up to no good!}
{You may swap any two players' cards without peeking, except your own.

Those players will assume those roles during the day, \\unbeknownst to themselves.}{Yes}}
%
{\townsfolk{Drunk}
{I'm not drunk, I swear!}
{You must swap your card with a centre card, without looking at your new role.}{Yes}}

\newpage
\reversecardpage

\newpage
\cardpage{%
\townsfolk{Insomniac}
{Can't stay asleep.}
{Wake up last in the night to see if your card is still the same, if not, you assume your new role in the day.}{Yes}}
%
{\townsfolk{Mason}
{A secret bond.}
{Wake up in the night to find your fellow mason, you know you're both good, now convince the others...}{Yes}}
%
{\townsfolk{Mason}
{A secret bond.}
{Wake up in the night to find your fellow mason, you know you're both good, now convince the others...}{Yes}}
%
{\selfish{Tanner}
{There's no `I' in team!}
{Your sole goal is to get yourself killed, you play for no team other than yourself. 

Play it carefully, otherwise the townsfolk may catch on to your scheming.}{No}}
%
{\townsfolk{Hunter}
{Take `em down with you!}
{If you are killed during the vote at the end of the day, whomever you are pointing to dies as well.}{No}}
%
{\townsfolk{Doppelgänger}
{Oh you chameleon, you!}
{You wake up first, view another player's card and assume their role, without exchanging cards.}{Yes}}
%
{\werewolf{Minion}
{You serve the darkness.}
{You are team werewolf, but they don't know who you are. When you wake up, look out for those furry thumbs. 

Your goal is to keep the werewolves alive at all costs, your life is worthless.}{Yes}}
%
{\townsfolk{Villager}
{Hunt the wolves!}
{\villagerDescription}{No}}
%

\newpage
\reversecardpage

\end{document}
